---
graphics: yes
name: Beau
surname: Hilton
headcolor: 414141
#qualifications:
position: "Physician data-scientist"
address: "303 Light Hall, 2215 Garland Ave. Nashville, TN 37232"
phone: "+1 623-332-7978"
www: beauhilton.com
email: "beau@beauhilton.com"
github: cbeauhilton
# aboutme: Physician, data scientist.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa6-cv.csl"
nocite: "@*"
knit: "bookdown::render_book"
output:
  vitae::awesomecv:
    fig_caption: yes
    keep_tex: no
    keep_md: no
    pandoc_args:
      #- --lua-filter="lua/multiple-bibliographies.lua"
      - --lua-filter="lua/strong.lua"
bibliography_journals: "bib/journal.bib"
bibliography_abstracts: "bib/poster_abstract.bib"
bibliography_oral_abstracts: "bib/oral_abstract.bib"
# bibliography_contribute: "bib/contribute.bib"
# bibliography_selected: "bib/selected.bib"
# bibliography_wip_journal: "bib/wip_journal.bib"
# bibliography_wip_proceeding: "bib/wip_proceeding.bib"
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[R]{\thepage}
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(ezpickr)
```

<!--chapter:end:index.Rmd-->

# Education

```{r education}
ezpickr::pick("data/education.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:education.Rmd-->

# Work Experience

```{r working-experience}
ezpickr::pick("data/working-experience.csv") %>%
  dplyr::filter(highlight == 1) %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why, .protect = FALSE)
```

<!--chapter:end:work_exp.Rmd-->

# Professional Appointments

```{r appointment}
ezpickr::pick("data/appointment.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:appointment.Rmd-->

# Publications

::: {#refs_journals}
:::

<!-- ## Working Papers under Revision or Review -->
<!--  -->
<!-- ::: {#refs_working_paper} -->
<!-- ::: -->

<!--  ::: {#refs_proceedings} -->
<!-- ::: -->

<!--chapter:end:publication.Rmd-->

# Presentations

```{r talk}
ezpickr::pick("data/talk.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why, .protect = TRUE)
```

<!--chapter:end:presentation.Rmd-->

# Abstracts

::: {#refs_abstracts}
:::

<!--chapter:end:abstract.Rmd-->

# Research Experience

```{r research-experience}
ezpickr::pick("data/research-experience.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:research_exp.Rmd-->

# Grants

```{r grant}
ezpickr::pick("data/grant.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:grant.Rmd-->

# Awards and Honors

```{r award}
ezpickr::pick("data/award.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:award.Rmd-->

# Teaching Experience

```{r teaching-experience}
ezpickr::pick("data/teaching-experience.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:teaching_exp.Rmd-->

# Service

```{r service}
ezpickr::pick("data/service.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:service.Rmd-->

# Current Memberships

  * American Society of Hematology
  * American Society of Clinical Oncology
  * American College of Physicians

<!--chapter:end:membership.Rmd-->

# Notes

* This CV is reproducible:
  source code available on this GitHub repository: <https://github.com/cbeauhilton/cv>, 
  which borrowed heavily from JooYoung Seo's CV project: <https://github.com/jooyoungseo/jy_CV>.

<!--chapter:end:backmatter.Rmd-->

